### 2020-05-28 writeup/proof_examples.tex
reorder

We first prove Proposition \ref{prop_data_size}, which describes the effect of source task data size on the information transfer.

@@

\subsection{Proofs for Section \ref{sec_covariate}}\label{app_covariate}

@@

>>>>

Then we prove Proposition \ref{prop_data_size}, which describes the effect of source task data size on the information transfer.

@@

@@

%\subsection{Proofs for Section \ref{sec_covariate}}\label{app_covariate}

### 2020-05-28 writeup/transfer.tex
reorder

\subsection{Contributing Causes of Negative Transfer}

@@

The proof of Proposition \ref{prop_data_size} is similar to Proposition \ref{prop_dist_transition}.
We compare the model shift bias and the amount of reduced variance of $\hat{\beta}_t^{\MTL}$.
An intuitive interpretation of Proposition \ref{prop_data_size} is that:
i) If the two task models are sufficiently similar (as specified under the first bullet), adding the source task always provides positive transfer;
ii) Otherwise, as we increase the number of source task data points, the transfer is positive initially, but transitions to negative eventually.
We leave the proof of Proposition \ref{prop_data_size} to Appendix \ref{app_proof_data}.

@@

	In Figure \ref{fig_covariate}, we plot the test error of the target task for $n_2 = 4p$ and $n_1$ ranging from $p$ to $20p$.
	Second, we observe the following two phases as we increase $n_1 / p$.
	When $n_1 \le n_2$, having complementary covariance matrices leads to lower test error compared to the case when $\Sigma_1 = \Sigma_2$.
	When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
	A theoretical justification can be found in Appendix \ref{app_covariate}.
\end{example}

@@

\begin{proposition}\label{prop_var_transition}
	In the simplified model with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 50$ is a fixed constant and $d^2 < \frac {\sigma_2^2} {2p} \cdot \Phi(\rho_1, \rho_2)$.
	We derive the following transition as a parameter of $\sigma_1^2$:
	\begin{itemize}
		\item If $\sigma_1^2 \le -\frac32 \rho_1 \cdot p d^2+\left(1+ \frac34\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If $\sigma_1^2 > - \frac12\rho_1\cdot p d^2   +\left(1+ \frac32\rho_1\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{proposition}
As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
The proof of Proposition \ref{prop_var_transition} is similar to Proposition \ref{prop_dist_transition}.
The details can be found in Appendix \ref{app_proof_31}.

>>>>

\subsection{Contributing Causes of Negative Transfer}\label{sec_similarity}

@@

The proof of Proposition \ref{prop_data_size} is similar to Proposition \ref{prop_dist_transition}.
We compare the model shift bias and the amount of reduced variance of $\hat{\beta}_t^{\MTL}$.
An intuitive interpretation of Proposition \ref{prop_data_size} is that:
i) If the two task models are sufficiently similar (as specified under the first bullet), adding the source task always provides positive transfer;
ii) Otherwise, as we increase the number of source task data points, the transfer is positive initially, but transitions to negative eventually.
We leave the proof of Proposition \ref{prop_data_size} to Appendix \ref{app_proof_31}.

@@

	In Figure \ref{fig_covariate}, we plot the test error of the target task for $n_2 = 4p$ and $n_1$ ranging from $p$ to $20p$.
	Second, we observe the following two phases as we increase $n_1 / p$.
	When $n_1 \le n_2$, having complementary covariance matrices leads to lower test error compared to the case when $\Sigma_1 = \Sigma_2$.
	When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
	A theoretical justification can be found in Appendix \ref{app_proof_31}.
\end{example}

@@

\begin{proposition}\label{prop_var_transition}
	In the simplified model with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 50$ is a fixed constant and $d^2 < \frac {\sigma_2^2} {2p} \cdot \Phi(\rho_1, \rho_2)$.
	We derive the following transition as a parameter of $\sigma_1^2$:
	\begin{itemize}
		\item If $\sigma_1^2 \le -\frac32 \rho_1 \cdot p d^2+\left(1+ \frac34\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If $\sigma_1^2 > - \frac12\rho_1\cdot p d^2   +\left(1+ \frac32\rho_1\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{proposition}
As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
The proof of Proposition \ref{prop_var_transition} is similar to Proposition \ref{prop_dist_transition}.
The details can be found in Appendix \ref{app_proof_data}.
